%-------------------------
% CV Template in LaTeX
% Author: Ashmit JaiSarita Gupta (https://ashmit.dev/)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% Serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\vspace*{1pt}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ashmit Gupta} \\ \vspace{1pt}
    H.No. 30, Gurutola, Azamgarh, Uttar Pradesh 276001 \\ \vspace{1pt}
    \href{tel:+91-8299538244}{\raisebox{-0.2\height}\faPhone\  \underline{+91-8299538244}} ~
    \href{https://www.ashmit.dev}{\raisebox{-0.2\height}\faGlobe\ 
    \underline{ashmit.dev}} ~
    \href{mailto:ashmitgupta.official@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ashmitgupta.official@outlook.com}} ~ 
    \href{https://www.linkedin.com/in/jaisarita/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jaisarita}}  ~
    
    \href{https://github.com/devilkiller-ag}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/devilkiller-ag}}
    \vspace{-8pt}
\end{center}

\vspace{6pt}

%------------SUMMARY------------
\section{Summary}
    An Engineering Physics Undergraduate with a strong passion for Web Development and Quantum Computing.

\vspace*{-2pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Hamirpur}{Dec. 2021 -- June 2025}
      {Bachelor of Technology in Engineering Physics}{Hamirpur, Himachal Pradesh}
    \resumeSubheading
      {Jyoti Niketan School}{April 2006 -- June 2020}
      {Primary and Secondary Education}{Azamgarh, Uttar Pradesh}
  \resumeSubHeadingListEnd

\vspace*{-2pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages}{: C++, JavaScript, TypeScript, Python} \\
            \textbf{Technologies/Frameworks}{: ReactJs, ExpressJs, Storybook, Qiskit, Pennylane, Classiq, PyTorch, Numpy, Matplotlib} \\
            \textbf{Domains}{: Data Structures and Algorithms, Full Stack Web Development, Quantum Computing, Community Management}
        }}
    \end{itemize}

\vspace*{-2pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {\href{https://summerofcode.withgoogle.com/programs/2024/projects/S49Gon9W}{Google Summer of Code 2024}}{May 2024 - Present}
        {Open Source Mentorship Program}{AsyncAPI Initiative}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{Developing a UI Kit for the AsyncAPI website using Storybook in Next.js and Typescript.}
        \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.asyncapi.com/}{Open Source Contributor at the AsyncAPI Intitative}}{Oct. 2023 - Present}
        {Web Developer and Technical Steering Committee Member}{AsyncAPI Initiative}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{I am a member of the AsyncAPI \underline{\href{https://www.asyncapi.com/community/tsc}{Technical Steering Committee}} which is responsible for the oversight of the AsyncAPI Initiative.}
            \resumeItem{Migrated the \underline{\href{https://www.asyncapi.com/}{AsyncAPI Website}} from JavaScript to TypeScript + Next.js.}
            \resumeItem{Migrated the \underline{\href{https://modelina.org/}{Modelina website}} codebase from class-based react components to functional components.}
            \resumeItem{Developed \underline{\href{https://modelina.org/playground}{Modelina Playground}} to enable visitors to try Modelina itself on the website without configuring something in the local environment.}
        \resumeItemListEnd
  
    \resumeSubheading
        {\href{https://creedandbear.com/}{Quantum Computing Intern}}{January 2024 - Present}
        {Internship}{Creed \& Bear}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{Working on quantum computing research and software projects.}
            \resumeItem{Currently developing software for portfolio optimization using quantum computing.}
            \resumeItem{Researched and wrote a review paper on the Effect of Quantum Computing on Blockchain.}
            \resumeItem{Worked on the Optimization of the Power Distribution Network at the three-month TCS Quantum Challenge 2023.}
        \resumeItemListEnd
            
    \resumeSubheading
        {\href{https://www.qaif.org/contests/quantum-games-hackathon}
        {Quantum Games Hackathon 2023}}{October 2023}
        {Participant}{Quantum AI Foundation}
        \resumeItemListStart
            \resumeItem{Developed \underline{\href{https://github.com/devilkiller-ag/QuantaVania}{QuantaVania}}, a 2D action-adventure platformer quantum game facilitating Quantum Computing learning.}
            \resumeItem{Winner of the Special Prize for Sanrto/Onyx Category for demonstrating Logistics optimization using QUBO in our game.}
        \resumeItemListEnd
        
    \resumeSubheading
            {\href{https://qworld.net/qcourse551-1/}
            {Quantum Software Developer Trainee}}{October 2023 - January 2024}
            {QCourse551 Mentorship Program with Classiq}{QWorld}
            \resumeItemListStart
                \resumeItem{Developing a hybrid network with classical and quantum layers to classify the MNIST dataset.}
                \resumeItem{Maintaining a weekly blog post about the project journey at \underline{\href{https://jaisarita.hashnode.dev/reflection-on-my-quantum-software-developer-journey-at-qworld-classiq-implementing-quantum-neural-network-algorithm}{https://jaisarita.hashnode.dev/}}.}
            \resumeItemListEnd

    \newpage
    
    \resumeSubheading
        {\href{https://qiskit.org/advocates}
        {Qiskit Advocate}}{August 2023 - Present}
        {Developer Advocate}{Qiskit}
        \resumeItemListStart
            \resumeItem{Resolved Bugs in Qiskit Braket Provider and Qiskit Textbook.}
            \resumeItem{Achieved certification as IBM Certified Associate Developer - Quantum Computation using Qiskit v0.2X}
        \resumeItemListEnd
    
    \resumeSubheading
    {\href{https://qworld.net/qintern-2023/}
      {QIntern 2023}}{July 2023 - August 2023}
      {Research Intern}{QWorld}
      \resumeItemListStart
        \resumeItem{Optimized logistics using quantum computing.}
        \resumeItem{Solved Vehicle Routing Problem using VQE, Surrogate Optimization, and their variants.}
      \resumeItemListEnd
      
      \resumeSubheading
      {\href{https://sites.nyuad.nyu.edu/hackathon/}
      {11th NYUAD International Hackathon For Social Good}}{April 2023}
      {Participant}{New York University Abu Dhabi}
      \resumeItemListStart
        \resumeItem{Attended workshops on QBronze and QSilver.}
        \resumeItem{Built an application to use Quantum Computing for Simulating Molecular Engineering for Fertilizer Design.}
      \resumeItemListEnd

      \resumeSubheading
        {\href{https://studentambassadors.microsoft.com/en-US/studentambassadors/profile/5712f83a-b4c5-4033-b77a-a5ce2bbd6ea3}{Microsoft Learn Student Ambassador}}{October 2022 -- Present}
        {Beta Microsoft Learn Student Ambassador}{Hamirpur}
        \resumeItemListStart
            \resumeItem{Completed the Technical Onboarding Process and learned about Git, GitHub, and Static Web Apps.}
            \resumeItem{Reached Alpha Milestone by completing Microsoft Learn Learning Path on Quantum Computing.}
            \resumeItem{Conducted a Microsoft Student Ambassadors Azure AI Challenge at my department with 24 attendees.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace*{1pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\href{https://pypi.org/project/qcge/}{Open Source Contribution}} $|$ \emph{AsyncAPI, Uptane, Qiskit}}{}
            \resumeItemListStart
                \resumeItem{Developed Modelina Playground, Modelina CLI, and Modelina Website. Migrated the AsyncAPI website from JavaScript to TypeScript. I am a Technical Steering Committee Member, a Maintainer, and a regular contributor at the AsynCAPI Initiative.}
                \resumeItem{Contributed to CI/CD and currently integrating Tailwind to Uptane Website.}
            \resumeItemListEnd
            \vspace{-13pt}
            
            % {\textbf{\href{https://pypi.org/project/qcge/}{QCGE: Quantum Circuit Game Engine}} $|$ \emph{Qiskit, Pygame}}{Nov 2023}
            % \resumeItemListStart
            %     \resumeItem{Developed QCGE, a Python package facilitating game developers to integrate Quantum Circuits into Pygame-based quantum games seamlessly.}
            %     \resumeItem{Enables easy addition of controls based on quantum circuits and measurements, with customizable UI, qubit count, and gate configurations.}
            % \resumeItemListEnd
            % \vspace{-13pt}
        
        \resumeProjectHeading
            {\textbf{\href{https://github.com/devilkiller-ag/QuantaVania}{QuantaVania}} $|$ \emph{Qiskit, Pygame}}{Oct 2023}
            \resumeItemListStart
                \resumeItem{Designed QuantaVania, an action-adventure 2D platformer with the potential for evolving into an open-world sandbox.}
                \resumeItem{Winner of the Special Prize by Snarto/Onyx at the Quantum Games Hackathon 2023.}
            \resumeItemListEnd
            \vspace{-13pt}

        \resumeProjectHeading
            {\textbf{\href{https://ashmit.dev/}{Portfolio Website}} $|$ \emph{Figma, React, Typescript, Three.js, TailwindCSS, EmailJS, GraphQL, HyGraph}}{July - August 2023}
            \resumeItemListStart
                \resumeItem{Developed a portfolio website for myself having features to write blogs, and showcase my projects, experiences, and resume in an interactive way using 3D components.}
            \resumeItemListEnd
            \vspace{-13pt}
        
        \resumeProjectHeading
            {\textbf{\href{https://askitout.vercel.app/}{AskItOut: Doubt Sharing Website for Educational Institutions}} $|$ \emph{Figma, React, Express.js}}{Feb - May 2023}
            \resumeItemListStart
                \resumeItem{Designed and developed a website enabling college students to ask and get answers to their doubts from experienced seniors.}
                \resumeItem{Code and detailed description available at \underline{{\href{https://github.com/devilkiller-ag/AskItOut}{https://github.com/devilkiller-ag/AskItOut}}}.}
            \resumeItemListEnd
            \vspace{-13pt}
            
            \resumeProjectHeading
                {\textbf{\href{https://github.com/devilkiller-ag/NYUAD-2023/tree/main/QCrop}{QCrop}} $|$ \emph{Qiskit, React, Python}}{April 2023}
                \resumeItemListStart
                  \resumeItem{Developed QCrop, an application utilizing Quantum Computing to simulate molecular engineering for fertilizer design.}
                  \resumeItem{Utilized Variational Quantum Eigensolver and Error Mitigation Techniques for calculating the energy landscape of different molecules.}
                \resumeItemListEnd
                \vspace{-13pt}
            
        \resumeProjectHeading
            {\textbf{\href{https://github.com/devilkiller-ag/Quantum-Breakout}{Quantum Breakout}} $|$ \emph{Pygame, Qiskit, Python}}{March 2023}
            \resumeItemListStart
                \resumeItem{Created a Quantum version of the classical Breakout Game, aiding school students in learning Qubit Manipulation using different Quantum Gates.}
            \resumeItemListEnd
            \vspace{-13pt}
            
        \resumeProjectHeading
            {\textbf{\href{https://abraxas-2023.vercel.app/}{Website for Team Abraxas}} $|$ \emph{Figma, ReactJs, react-three-fiber, react-three-drei}}{March 2023}
            \resumeItemListStart
                \resumeItem{Developed the official website of Team Abraxas for the annual tech-fest Nimbus 2023 at NIT Hamirpur.}
            \resumeItemListEnd
            \vspace{-13pt} 
            
        \resumeProjectHeading
            {\textbf{\href{https://ashmit.dev/archives}{Explore All Projects}} \emph{}}{}
            \resumeItemListStart
                \resumeItem{Visit \underline{{\href{https://ashmit.dev/archives}{https://ashmit.dev/archives}}} to explore all my projects in detail.}
            \resumeItemListEnd
            \vspace{-13pt} 

    \resumeSubHeadingListEnd

% \vspace{10pt}

% ---------------- OTHER COURSES ---------------------
% \section{Other Courses}
%         \begin{multicols}{2}
%             \begin{itemize}[itemsep=2pt, parsep=3pt]
%                 \item\small Qbronze and QSilver at Womanium Quantum 2022
%                 \item\small Technical Introduction to Quantum Computing Hardware
%                 \item The Fundamentals of Digital Marketing by Google
%                 \item Introduction to UI UX by Great Learnings
%                 \item IBM Enterprise Design Thinking
%                 \item Introduction to Cloud Computing by IBM
%                 \item DevOps Essentials by IBM
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}

% \vspace{10pt}

% ---------------- Workshops and Events Hosted ---------------------
\section{Workshops and Events Hosted}
    \resumeSubHeadingListStart
        \resumeSubheading{Quantum Breakout Game: Revolutionizing Quantum Learning Through Gamification}{23rd Nov 2023}{Speaker at the Data Science Summit 2023}{VoD}
            \resumeItemListStart
                \resumeItem{Delivered an overview of Quantum Computing, addressing challenges faced by newcomers.}
                \resumeItem{Explored the role of quantum games in overcoming learning obstacles beginners face, featuring a live demonstration of Quantum Breakout Game and QCGE.}
            \resumeItemListEnd 

        \resumeSubheading{Surrogate Optimization for QUBO solver using QROSS Method}{23rd Nov 2023}{Speaker at the Data Science Summit 2023}{VoD}
            \resumeItemListStart
                \resumeItem{Presented an overview of research on Surrogate Optimization for QUBO Solver as a QIntern at QWorld.}
            \resumeItemListEnd 

        \resumeSubheading{QuantaVania: A Quantum Computing Sandbox Platformer Game}{23rd Nov 2023}{Speaker at the Data Science Summit 2023}{VoD}
            \resumeItemListStart
                \resumeItem{Presented the journey at the Quantum Games Hackathon 2023 and QuantaVania, illustrating its transformation into a Sandbox game for running in-game quantum circuits on real quantum devices.}
            \resumeItemListEnd 
        
        \resumeSubheading{Introductory Workshop on Quantum Computing}{4th February 2023}{Team Abraxas}{Nimbus 2023}
            \resumeItemListStart
                \resumeItem{Conducted a Workshop on The Introduction to Quantum Computing, instructing 100+ students about the basics and career opportunities.}
            \resumeItemListEnd 

        \resumeSubheading{Reimagining Education in Light of NEP 2020}{20th April 2023}{Physteo}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Organized the first workshop by Physteo - The Physics Society of NIT Hamirpur.}
                \resumeItem{Facilitated talks by Prof. B.N. Jagatap and Prof. B.P. Singh on National Education Policy, Laser Photonics, Entrepreneurship, and career Paths for Engineering Physics Students.}
            \resumeItemListEnd 
    \resumeSubHeadingListEnd

\vspace*{1pt}

% ---------------- Leadership / Volunteering ---------------------
\section{Leadership / Volunteering}
    \resumeSubHeadingListStart
        \resumeSubheading{Physteo - The Physics Society}{Oct. 2022 -- Present}{Founder and President}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Founded the Physics Society of the National Institute of Technology Hamirpur under the Department of Physics and Photonics Science.}
                \resumeItem{Organizing National Physics Conference 2024 to bring top representatives of Industry and Academia working in the different fields of Physics to one platform and guide the students.}
                \resumeItem{Leading and managing the team of 60 individuals to promote our department in the industry world and guide our students.}
            \resumeItemListEnd

        \resumeSubheading{UbuCon Asia 2024}{May 2024 -- September 2024}{Volunteer}{Ubuntu Asia Community}
            \resumeItemListStart
                \resumeItem{Organizing UbuCon Asia 2024 at Jaipur, India.}
                \resumeItem{Handling the Website Development, Sponsorship, and Management Role.}
            \resumeItemListEnd

        \resumeSubheading{Training and Placement Office}{August 2023 -- September 2024}{Training and Placement Representative (TPR)}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Currently serving as a Core TPR managing industry and institute interaction and database.}
                \resumeItem{Served as Junior TPR during my pre-final year undergraduate studies from August 2023 - April 2024. I helped pre-final year students to grab internships by bringing and coordinating with various companies.}
            \resumeItemListEnd
                
        \resumeSubheading{Team Abraxas}{Dec. 2022 -- Present}{Executive Volunteer and Pre-final year Volunteer}{Nimbus 2023 and Nimbus 2024}
            \resumeItemListStart
                \resumeItem{Conducted a workshop on the Introduction to Quantum Computing, instructing 100+ students about the basics and career opportunities.}
                \resumeItem{Developed a 2-D game, Quantum Breakout, to simplify learning Quantum Gates.}
                \resumeItem{Leading and guiding freshmen and sophomore volunteers.}
            \resumeItemListEnd 

        \resumeSubheading{Society for Promotion of Electronics Culture}{Dec. 2021 -- Jan. 2023}{Executive Volunteer}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Organized Electrothon 4.0, a global online hackathon with 2000+ participants.}
                \resumeItem{Created content for social media posts, emails, and speeches for various society events.}
                \resumeItem{Organized and hosted workshops to give attendees an insight into the engineering industry.}
            \resumeItemListEnd 
    \resumeSubHeadingListEnd

\vspace*{1pt}

\newpage

% ---------------- Hackathons and Events Attended ---------------------
\section{Hackathons and Events Attended}
    \begin{multicols}{2}
        \begin{itemize}[itemsep=2pt, parsep=3pt]
            \item\small Qubit by Qubit Winter Break Intensive
            \item Electrothon 4.0
            \item Smart India Hackathon 2022
            \item Womanium Global Quantum Computing and Entrepreneurship Program 2022
            \item Hacktoberfest 2022
            \item MIT iQHack 2023
            \item Xanadu QHack 2023
            \item Nimbus 2023
            \item Electrothon 5.0
            \item 11th NYUAD International Hackathon for Social Good
            \item Qiskit Spring Challenge 2023
            \item UnitaryHACK 2023
            \item Quantum Game Jam 2023
            \item Quantum Games Hackathon 2023
            \item Hacktoberfest 2023
            \item TCS Quantum Challenge 2023-24
            \item Nimbus 2024
        \end{itemize}
    \end{multicols}
    \vspace*{2.0\multicolsep}

\end{document}
