%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------
% CV Template in LaTeX
% Author: Ashmit JaiSarita Gupta (https://ashmit.dev/)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}
\usepackage{fontawesome5}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% Serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
        \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{#1} & \textbf{\small #2} \\
            \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}
        \vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\vspace*{1pt}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ashmit Gupta} \\ \vspace{1pt}
    H.No. 30, Gurutola, Azamgarh, Uttar Pradesh 276001 \\ \vspace{1pt}
    \href{tel:+91-8299538244}{\raisebox{-0.2\height}\faPhone\  \underline{+91-8299538244}} ~
    \href{https://www.ashmit.dev}{\raisebox{-0.2\height}\faGlobe\ 
    \underline{ashmit.dev}} ~
    \href{mailto:ashmitgupta.official@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ashmitgupta.official@outlook.com}} ~ 
    \href{https://www.linkedin.com/in/jaisarita/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jaisarita}}  ~
    
    \href{https://github.com/devilkiller-ag}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/devilkiller-ag}}
    % \vspace{-4pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {National Institute of Technology Hamirpur}{Dec. 2021 -- July 2025}
            {Bachelor of Technology in Engineering Physics}{Hamirpur, Himachal Pradesh}
    \resumeSubHeadingListEnd
    
\vspace{-8pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages}{: C++, JavaScript, TypeScript, Python} \\
            \textbf{Technologies/Frameworks}{: ReactJs, ExpressJs, Storybook, Qiskit, Pennylane, Classiq, PyTorch, Numpy, Matplotlib} \\
            \textbf{Domains}{: Data Structures and Algorithms, Full Stack Web Development, Quantum Computing, Community Management}
        }}
    \end{itemize}

\vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
    {\href{https://summerofcode.withgoogle.com/programs/2024/projects/S49Gon9W}{Google Summer of Code 2024}}{May 2024 - Present}
        {Open Source Mentorship Program}{AsyncAPI Initiative}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{Developing a UI Kit for the AsyncAPI website using Storybook in Next.js and Typescript.}
        \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.asyncapi.com/}{Open Source Contributor at the AsyncAPI Intitative}}{Oct. 2023 - Present}
        {Web Developer and Technical Steering Committee Member}{AsyncAPI Initiative}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{I am a member of the AsyncAPI \underline{\href{https://www.asyncapi.com/community/tsc}{Technical Steering Committee}} which is responsible for the oversight of the AsyncAPI Initiative.}
            \resumeItem{Migrated the \underline{\href{https://www.asyncapi.com/}{AsyncAPI Website}} from JavaScript to TypeScript + Next.js.}
            \resumeItem{Migrated the \underline{\href{https://modelina.org/}{Modelina website}} codebase from class-based react components to functional components.}
            \resumeItem{Developed \underline{\href{https://modelina.org/playground}{Modelina Playground}} to enable visitors to try Modelina itself on the website without configuring something in the local environment.}
        \resumeItemListEnd
  
    \resumeSubheading
        {\href{https://creedandbear.com/}{Quantum Computing Intern}}{January 2024 - Present}
        {Internship}{Creed \& Bear}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{Working on quantum computing research and software projects.}
            \resumeItem{Currently developing software for portfolio optimization using quantum computing.}
            \resumeItem{Researched and wrote a review paper on the Effect of Quantum Computing on Blockchain.}
            \resumeItem{Worked on the Optimization of the Power Distribution Network at the three-month TCS Quantum Challenge 2023.}
        \resumeItemListEnd
        
        \resumeSubheading
            {\href{https://www.qaif.org/contests/quantum-games-hackathon}{Quantum Games Hackathon 2023}}{October 2023}
            {Participant}{Quantum AI Foundation}
            \vspace{-6pt}
            \resumeItemListStart
                \resumeItem{Developed \underline{\href{https://github.com/devilkiller-ag/QuantaVania}{QuantaVania}}, a 2D action-adventure platformer quantum game facilitating Quantum Computing learning.}
                \resumeItem{Winner of the Special Prize for Sanrto/Onyx Category for demonstrating Logistics optimization using QUBO in our game.}
            \resumeItemListEnd
        
        \resumeSubheading
            {\href{https://qworld.net/qcourse551-1/}{Quantum Software Developer Trainee}}{October 2023 - January 2024}
            {QCourse551 Mentorship Program with Classiq}{QWorld}
            \vspace{-6pt}
            \resumeItemListStart
                \resumeItem{Developing a hybrid network with classical and quantum layers to classify the MNIST dataset.}
                \resumeItem{Maintaining a weekly blog post about the project journey at \underline{\href{https://jaisarita.hashnode.dev/reflection-on-my-quantum-software-developer-journey-at-qworld-classiq-implementing-quantum-neural-network-algorithm}{https://jaisarita.hashnode.dev/}}.}
            \resumeItemListEnd
  
        \resumeSubheading
            {\href{https://qiskit.org/advocates}{Qiskit Advocate}}{August 2023 - Present}
            {Developer Advocate}{Qiskit}
            \vspace{-6pt}
            \resumeItemListStart
                \resumeItem{Resolved Bugs in Qiskit Braket Provider and Qiskit Textbook.}
                \resumeItem{Achieved certification as IBM Certified Associate Developer - Quantum Computation using Qiskit v0.2X}
            \resumeItemListEnd

        \resumeSubheading
            {\href{https://studentambassadors.microsoft.com/en-US/studentambassadors/profile/5712f83a-b4c5-4033-b77a-a5ce2bbd6ea3}
            {Microsoft Learn Student Ambassador}}{October 2022 -- Present}
            {Beta Microsoft Learn Student Ambassador}{Hamirpur}
            \vspace{-6pt}
            \resumeItemListStart
                \resumeItem{Completed the Technical Onboarding Process and learned about Git, GitHub, and Static Web Apps.}
                \resumeItem{Reached Alpha Milestone by completing Microsoft Learn Learning Path on Quantum Computing.}
                \resumeItem{Conducted a Microsoft Student Ambassadors Azure AI Challenge at my department with 24 attendees.}
                \resumeItemListEnd
            
        \resumeSubheading
            {\href{https://qworld.net/qintern-2023/}{QIntern 2023}}{July 2023 - August 2023}
            {Research Intern}{QWorld}
            \vspace{-6pt}
            \resumeItemListStart
                \resumeItem{Optimized logistics using quantum computing.}
                \resumeItem{Solved Vehicle Routing Problem using VQE, Surrogate Optimization, and their variants.}
            \resumeItemListEnd

        \resumeSubheading
        {\href{https://sites.nyuad.nyu.edu/hackathon/}{11th NYUAD International Hackathon For Social Good}}{April 2023}{Participant}{New York University Abu Dhabi}
        \vspace{-6pt}
        \resumeItemListStart
            \resumeItem{Attended workshops on QBronze and QSilver.}
            \resumeItem{Built an application to use Quantum Computing for Simulating Molecular Engineering for Fertilizer Design.}
        \resumeItemListEnd
        % \vspace{-4pt}
    
    \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\href{https://ashmit.dev/}{Portfolio Website}} $|$ \emph{Figma, React, Typescript, Three.js, TailwindCSS, EmailJS, GraphQL, HyGraph}}{July - August 2023}
            \resumeItemListStart
                \resumeItem{Developed a portfolio website for myself having features to write blogs, and showcase my projects, experiences, and resume in an interactive way using 3D components.}
            \resumeItemListEnd
            \vspace{-15pt}
        
        % \resumeProjectHeading
            % {\textbf{\href{https://pypi.org/project/qcge/}{QCGE: Quantum Circuit Game Engine}} $|$ \emph{Qiskit, Pygame}}{Nov 2023}
            % \resumeItemListStart
            %     \resumeItem{Developed QCGE, a Python package facilitating game developers to integrate Quantum Circuits into Pygame-based quantum games seamlessly.}
            %     % \resumeItem{Enables easy addition of controls based on quantum circuits and measurements, with customizable UI, qubit count, and gate configurations.}
            % \resumeItemListEnd
            % \vspace{-15pt} 
        
        \resumeProjectHeading
            {\textbf{\href{https://askitout.vercel.app/}{AskItOut: Doubt Sharing Website for Educational Institutions}} $|$ \emph{Figma, React, Express.js}}{Feb - May 2023}
            \resumeItemListStart
                \resumeItem{Designed and developed a website for college students to ask and get answers to their doubts from experienced seniors.}
                \resumeItem{Code and detailed description available at \underline{{\href{https://github.com/devilkiller-ag/AskItOut}{https://github.com/devilkiller-ag/AskItOut}}}.}
            \resumeItemListEnd
            \vspace{-15pt}
            
            \resumeProjectHeading
                {\textbf{\href{https://github.com/devilkiller-ag/NYUAD-2023/tree/main/QCrop}{QCrop}} $|$ \emph{Qiskit, React, Python}}{April 2023}
                \resumeItemListStart
                  \resumeItem{An application to use Quantum Computing for Simulating Molecular Engineering for Fertilizer Design.}
                  \resumeItem{Used Variational Quantum Eigensolver and Error Mitigation Techniques to calculate Energy Landscape of different molecules}
                \resumeItemListEnd
                \vspace{-13pt}

        % \resumeProjectHeading
        %     {\textbf{\href{https://github.com/devilkiller-ag/kullu-history-threejs}{Exploring the Past: Kullu}} $|$ \emph{Solidity, Blender 3D, HTML, Tailwind CSS, Javascript, Three.js, React}}{April 2023}
        %     \resumeItemListStart
        %         \resumeItem{Developed a website to promote tourism in Kullu, providing immersive VR experiences and increasing awareness of cultural and historical sites. Implemented a 3D NFT Marketplace for buying traditional and cultural art in the virtual world. }
        %     \resumeItemListEnd
        % \vspace{-13pt}
        
        \resumeProjectHeading
        {\textbf{\href{https://github.com/devilkiller-ag/Quantum-Breakout}{Quantum Breakout}} $|$ \emph{Pygame, Qiskit, Python}}{March 2023}
        \resumeItemListStart
        \resumeItem{Created a Quantum version of the classical Breakout Game to facilitate easy learning of Qubit Manipulation using various Quantum Gates.}
        \resumeItemListEnd
        \vspace{-15pt}
        
        % \resumeProjectHeading
        %     {\textbf{\href{https://abraxas-2023.vercel.app/}{Website for Team Abraxas}} $|$ \emph{Figma, ReactJs, react-three-fiber, react-three-drei}}{March 2023}
        %     \resumeItemListStart
        %         \resumeItem{Developed the official website of Team Abraxas for the annual tech-fest at NIT Hamirpur: Nimbus 2023.}
        %     \resumeItemListEnd
        % \vspace{-15pt} 
        
        \resumeProjectHeading
            {\textbf{\href{https://ashmit.dev/archives}{Explore All Projects}} \emph{}}{}
            \resumeItemListStart
                \resumeItem{Visit \underline{{\href{https://ashmit.dev/archives}{https://ashmit.dev/archives}}} to explore all my projects in detail.}
            \resumeItemListEnd
        \resumeSubHeadingListEnd

\vspace{-8pt}
        
%-----------INVOLVEMENT---------------
\section{Leadership / Volunteering}
    \resumeSubHeadingListStart
        \resumeSubheading{Physteo - The Physics Society}{Oct. 2022 -- Present}{Founder and President}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Founded the Physics Society of the National Institute of Technology Hamirpur under the Department of Physics and Photonics Science.}
                \resumeItem{Organizing National Physics Conference 2024 to bring top representatives of Industry and Academia working in the different fields of Physics to one platform and guide the students.}
                \resumeItem{Leading and managing the team of 60 individuals to promote our department in the industry world and guide our students.}
            \resumeItemListEnd

        \resumeSubheading{Training and Placement Office}{August 2023 -- September 2024}{Training and Placement Representative (TPR)}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Currently serving as a Core TPR managing industry and institute interaction and database.}
                \resumeItem{Served as Junior TPR during my pre-final year undergraduate studies from August 2023 - April 2024. I helped pre-final year students to grab internships by bringing and coordinating with various companies.}
            \resumeItemListEnd
                
        \resumeSubheading{Team Abraxas}{Dec. 2022 -- Present}{Executive Volunteer and Pre-final year Volunteer}{Nimbus 2023 and Nimbus 2024}
            \resumeItemListStart
                \resumeItem{Conducted a workshop on the Introduction to Quantum Computing, instructing 100+ students about the basics and career opportunities.}
                \resumeItem{Developed a 2-D game, Quantum Breakout, to simplify learning Quantum Gates.}
                \resumeItem{Leading and guiding freshmen and sophomore volunteers.}
            \resumeItemListEnd 

        \resumeSubheading{Society for Promotion of Electronics Culture}{Dec. 2021 -- Jan. 2023}{Executive Volunteer}{NIT Hamirpur}
            \resumeItemListStart
                \resumeItem{Organized Electrothon 4.0, a global online hackathon with 2000+ participants.}
                \resumeItem{Created content for social media posts, emails, and speeches for various society events.}
                \resumeItem{Organized and hosted workshops to give attendees an insight into the engineering industry.}
            \resumeItemListEnd 
    \resumeSubHeadingListEnd

\end{document}
